Embodied Neuromorphic Benchmarks

### 2015-08-16 paper/paper.tex
Merged last of Chris' edits! And a whole 20 mins left to the deadline...

@@

The approach to benchmarking presented here can also be applied to other tasks,
defining minimal simulations and evaluating hardware across a random sampling
of that space.

The most straightforward expansion would be to consider motor control where
the state being controlled \emph{is not the motor state itself}.  That is,
suppose we want to control the position of a hand $x$, but our output $u$
only directly controls the joints $q$ of an arm.  The position of the hand $x$
is some function of $q$, but this function may be unknown or highly complex.
Crucially, there is a learning rule that is similar to the one discussed above
that can learn this mapping (\citealt{adaptiveJacobian}), and we have had
some success in using it for particular arm control tasks (\citealt{dewolf2014}).
This would give a benchmark with a much more flexible set of capabilities;
for example a non-neural version of this learning algorithm was able to
learn to control a robot arm to follow a certain path, given only the
visual feedback of where the tip of its hand was, without knowing the
geometry of its own hand or the position of the camera with relation to that
hand (\citealt{adaptiveJacobian}).  While it is unlikely that such a
system would work for \emph{any} possible sensorimotor combination, developing
such a benchmark could identify the space of such embodiments that a
particular algorithm running on particular neuromorphic hardware would be
good at controlling.

We also believe this approach to developing benchmarks would be applicable
to more complex and abstract tasks.  For example, much of the original work
on minimal simulation involved robot navigation and obstacle avoidance.  
\cite{Jakobi97evolutionaryrobotics} created a
minimal simulation of an environment with fixed walls, a mobile robot, and
various sensory systems.  A benchmark involving movement between locations
while avoiding collisions could be defined, and the environment could be
enhanced with moving obstacles and a richer set of sensors.  The eventual
goal would be to achieve reliable movement in an environment that includes
people.

Another direction to take this sort of benchmark would be classical and
operant conditioning.  This sort of learning is extremely common in living
creatures, and is vital for dealing with novel environments.  As such,
it is natural to define tasks involving learning the associates between
sensory events in the environment (akin to classical conditioning) and the
associations between actions and desired sensory states (akin to operant
conditioning).  Again, the approach of minimal simulation could be used
to generate random complex sensory mappings, and various neuromorphic
learning algorithms could be evaluated in terms of their ability to
discern these patterns.  Importantly, this would also include the ability
to unlearn these patterns as the environment changes.  Interestingly, the
neuron-based classical conditioning learning rule used by \cite{verschure2003}
is quite similar to the learning rule used in the adaptive control benchmark
here.

@@

The primary purpose of this paper is to describe a new method for benchmarking
neuromorphic hardware that addresses the problem of reliably benchmarking
in a complex task that involves interaction with an environment.  This
method involves building a ``minimal'' simulation; one that is extremely
simple in terms of required computation, but that has a high degree of
adjustable variability.  By benchmarking across that whole space of
possibilities, we can identify hardware that performs well across that whole
space, and is thus likely to be useful in real-world situations.  In order
to identify what real-world situations are covered by a minimal simulation,
we can calibrate the variability in that simulation with particular physical
systems.

We demonstrated this approach by defining a minimal simulation and a task
based around adaptive motor control.  We presented a basic algorithm that
can use neuromorphic hardware to improve performance on this task.  While this
algorithm can be run on a variety of hardware, other algorithms could also
be used on this task, and there are many implementation possibilities.
Importantly, by measuring performance while adjusting the distributions of
parameters in the benchmark, it is possible to characterize different aspects
of the hardware, identifying how different aspects of the task affect
performance for different hardware.  This was demonstrated by providing
five different benchmarks, each based on the same minimal simulation, but
setting parameters in different ways.  We believe this sort of flexibility
is important in a benchmark, as it lets researchers be explicit about what
their hardware is good at, while still using the same basic and shareable
benchmark framework.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{figures/SingleArmSystem}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:system} Figure \arabic{figure}.}{ 
     An abstract physical system that could be controlled.  In order to hold
     the joint $q$ at a desired angle $q_d$, a force must be applied to
     counteract the pull of gravity.  The magnitude of this force is a
 function of $q$ which can be learned.}
\end{figure}

>>>>

All three hardware systems drastically improve performance on this task, as
compared to the non-adaptive controller.

@@

The approach to benchmarking presented here can be applied to a wide variety of other tasks,
by defining different minimal simulations and evaluating hardware and algorithms across a random sampling
of simulation parameters.

One possibility is to consider motor control where
the state being controlled \emph{is not the motor state itself}.  That is,
suppose we want to control the position of a hand $x$, but our output $u$
only directly controls the joints $q$ of an arm.  The position of the hand $x$
is some function of $q$, but this function may be unknown or highly complex.
Crucially, there is a learning rule that is similar to the one discussed above
that can learn this mapping (\citealt{adaptiveJacobian}), and we have had
some success in using it for particular arm control tasks (\citealt{dewolf2014}).
This would give a benchmark with a much more flexible set of capabilities;
for example a non-neural version of this learning algorithm was able to
learn to control a robot arm to follow a certain path, given only the
visual feedback of where the tip of its hand was, without knowing the
geometry of its own hand, or the position of the camera with relation to that
hand (\citealt{adaptiveJacobian}).  While it is unlikely that such a
system would work for \emph{any} possible sensorimotor combination, developing
such a benchmark could identify the space of such embodiments that a
particular algorithm running on particular neuromorphic hardware would be
good at controlling.

More generally, we believe that this approach to developing benchmarks is applicable
to entirely different kinds of tasks.  For example, much of the original work
on minimal simulation involved robot navigation and obstacle avoidance.  
\cite{Jakobi97evolutionaryrobotics} created a
minimal simulation of an environment with fixed walls, a mobile robot, and
various sensory systems.  Using such a simulation, a benchmark involving movement between locations
while avoiding collisions could be defined, and the environment could be
enhanced with moving obstacles and a richer set of sensors.  The eventual
goal might be to achieve reliable movement in an environment that includes
people.

Another example is the application of this method to classical and
operant conditioning.  Conditioning effects are extremely common in living
creatures, and are clearly evident when animals are exposed to novel environments.  As such,
it is natural to define benchmark tasks involving learning the associations between
sensory events in the environment (akin to classical conditioning) and the
associations between actions and desired sensory states (akin to operant
conditioning).  Again, the approach of minimal simulation could be used
to generate random complex sensory mappings, and various neuromorphic
learning algorithms could be evaluated in terms of their ability to
discern these patterns.  Importantly, this would also include the ability
to unlearn these patterns as the environment changes.  Interestingly, the
neuron-based classical conditioning learning rule used by \cite{verschure2003}
is quite similar to the learning rule used in the adaptive control benchmark
here.

@@

We have described a new method for benchmarking
neuromorphic hardware that addresses the problem of reliably benchmarking
complex tasks that involve interaction with an environment.  This
method involves building a minimal simulation; a simulation that is extremely
simple in terms of required computation, but that has a high degree of
adjustable variability.  By benchmarking across a space of
possibilities, we can identify hardware that performs well across that
space, and is thus likely to be useful in real-world situations.  In order
to identify which real-world situations are covered by a minimal simulation,
we can tune the variability in the simulation to particular physical
systems.

We demonstrated this approach by defining a minimal simulation and a task
appropriate for adaptive motor control.  We presented an algorithm that
can use neuromorphic hardware to improve performance on this task over that
of a standard non-adaptive controller.  
Importantly, by measuring performance while adjusting the distributions of
parameters in the benchmark, it is possible to characterize different aspects
of the hardware, identifying how different aspects of the task affect
performance for different hardware.  This was demonstrated by providing
five different benchmarks, each based on the same minimal simulation, but
setting parameters in different ways.  We believe this sort of flexibility
is important in a benchmark method, as it lets researchers be explicit about what
their hardware is good at, while still using the same basic and shareable
benchmark framework.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{figures/SingleArmSystem}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:system} Figure \arabic{figure}.}{ 
     A simple example of a physical embodiment for control.  In order to hold
     the joint $q$ at a desired angle $q_d$, a force must be applied to
     counteract the pull of gravity.  The magnitude of this force is a
 function of $q$ which can be learned.}
\end{figure}
